Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-01-30 WSSSPE1_report/WSSSPE1_summary_report.tex

>>>>

\subsection{What are communities?}
\subsection{Challenges of community}
include metrics for community success (e.g., more external contributors than internal).
\subsection{Admirable scientific software communities}
\begin{itemize}
\item example communities
\item their (quick) origin stories.
\subsection{Resources for learning about software communities}
\begin{itemize}
\item academic fields studying communities (and software communities)
\item courses on online communities
\item books
\item need for software carpentry module on organizing communities?
\end{itemize}
